% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
% Adjusted for Chinese Support and XeLaTeX compilation

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{xeCJK} % Support for Chinese characters
\setCJKmainfont[BoldFont=SimHei]{SimSun} % Set the main font to SimSun, or any other preferred font

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

% 新命令，用于需要额外行的条目
\newcommand{\resumeSubheadingExtended}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \multicolumn{2}{l}{\small#5}  % 添加的额外信息行
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape 谈至存} \\ % Chinese Name
    \vspace{5pt}
    \textbf{电话:} +(86) 13402536577 \ \textbf{邮箱: }\href{mailto:tanzc9866@126.com}{tanzc9866@126.com} \ \href{https://github.com/SpartanTan}{Github}\\ % 邮件
\end{center}


%--- Insert sections of resume here ---
%-----------EDUCATION-----------
\section{教育经历}
  \resumeSubHeadingListStart
    \resumeSubheadingExtended
      {丹麦科技大学 - 硕士}{哥本哈根，丹麦}
      {机械电子工程}
      {GPA 3.76, Class rank 63/350, SAT 1510}{2021.01 -- 2023.12}  
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubheading
      {查尔姆斯理工大学（交换）- 硕士}{哥德堡，瑞典}
      {GPA 3.76, Class rank 63/350, SAT 1510}{2022.09 -- 2023.12}
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubheading
      {南京工程学院 - 本科}{江宁，南京}
      {GPA 3.47, 专业排名 10/162, SAT 1510}{2016.09 -- 2020.06}
  \resumeSubHeadingListEnd

%-----------Extracurriculars-----------
\section{Extracurricular Activities}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Student Government}{Sept. 2023 -- Jun. 2024}
      {Treasurer}{Brooklyn, NY}
      \resumeItemListStart
        \resumeItem{Developed budget proposals, collaborating with the student government team to plan major school events.}
        \resumeItem{Organized and led fundraising events, \textbf{raising over \$5,000} for school activities and projects.}
        \resumeItem{Managed the student government budget, ensuring accurate tracking and allocation of funds.}
    
      \resumeItemListEnd
      
    \resumeSubheading
      {Math Team}{Sept. 2022 -- Present}
      {Team Captain}{Brooklyn, NY}
      \resumeItemListStart
        \resumeItem{Competed in regional, state, and national-level math competitions\textbf{(NYCIML, NYCMTS).}}
        \resumeItem{Facilitated weekly study sessions to discuss high-level \textbf{Probability Theory, Geometry \& Algebra.}}
        \resumeItem{Led a 26-member math team as captain, overseeing strategy development and competition preparation.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Varsity Swim Team}{Sep. 2021 -- June 2024}
      {Team Captain}{Brooklyn, NY}
      \resumeItemListStart
        \resumeItem{Led the varsity swim team to its \textbf{inaugural section championship} through leadership and strategic planning.}
        \resumeItem{Mentored junior team members, providing guidance on proper techniques, race preparation, and sportsmanship.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------Experience-----------
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
    {支教}{2024.02 -- 2024.06}
    {\small 小学老师}{龙门乡塔哈村小学, 凉山彝族自治州}
    \resumeItemListStart
      \resumeItem{二年级语文老师，班主任；三、四年级英语老师}
      \resumeItem{期末成绩全县排名17，同类学校排名第5}
    \resumeItemListEnd

    \resumeSubheading
      {盖茨电子}{2020.09 -- 2020.10}
      {电子研发实习生}{苏州}
      \resumeItemListStart
        \resumeItem{车载空压机FOC算法调试}
        \resumeItem{Developed minimum viable product(MVP) capable of early-stage revenue generation.}
        \resumeItem{Received positive feedback from established brands like Buffalo Wild Wings for innovative sauce holder designs.}
        \resumeItem{Validated startup idea through market research and interview feedback as a part of Launch-X U-Michigan.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Private Math Tutor}{Sept. 2021 -- Present}
      {Team Captain}{Brooklyn, NY}
      \resumeItemListStart
        \resumeItem{Provided personalized tutoring sessions in algebra, calculus, and geometry to elementary \& middle-school students}
        \resumeItem{Developed lesson plans for diverse learning styles, leading to improvements by \textbf{upwards of 1.5 letter grades}.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd


\section{Awards}
    \resumeSubHeadingListStart
      \resumeSubheading
      {Speedo Scholastic All-American}{Aug. 2023 -- Present}
      {}{}
      \resumeItemListStart
      \vspace{-4mm}
        \resumeItem{National award given to student-athletes who achieve a \textbf{national time standard }while maintaining a 3.5+ GPA.}
      \resumeItemListEnd
      
    \resumeSubheading
      {National Junior Honor Society}{June 2023 -- Present}
      {}{}
      \resumeItemListStart
      \vspace{-4mm}
        \resumeItem{Award presented to students with outstanding achievements in academics, leadership, and community service.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------Courses-----------
\section{Classes}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \vspace{1mm}
     \textbf{Courses}{: AP Calulus BC, AP Chemistry, AP Physics, AP World History, AP U.S. History, AP Statistics, AP Literature} \\

    }}
 \end{itemize}

%-----------Skill and Interests-----------
\section{Skills \& Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \vspace{1mm}
     \textbf{Skills}{: Probability Theory, Web Design, Microsoft Excel, Microsoft Office} \\
     \vspace{1mm}
     \textbf{Interests}{: Photography, Creative Writing, Archery, New York Knicks} \\
     \vspace{1mm}

    }}
 \end{itemize}
 \begin{center}
    
\small 123-456-7890 $|$
\href{mailto:ADD EMAIL HERE@x.com}{\underline{andrew@gmail.com}} $|$
\href{ADD LINKEDIN PAGE HERE}{\underline{linkedin.com/in/andrew}} 
\end{center}

\end{document}
