% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
% Adjusted for Chinese Support and XeLaTeX compilation

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{xeCJK} % Support for Chinese characters
\setmainfont{Arial}  % 将主字体设置为 Arial
\setCJKmainfont[BoldFont=Microsoft YaHei]{SimSun} % Set the main font to SimSun, or any other preferred font
\usepackage{fontawesome}  % 加载 FontAwesome 图标库
\usepackage{multirow}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item\small{
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-7pt}
  }
}

% 新命令，用于需要额外行的条目
\newcommand{\resumeSubheadingExtended}[5]{  
  \item\small{
    \begin{tabular*}{0.97\textwidth}{@{}p{0.8\textwidth}p{0.52\textwidth}@{}}
    % \begin{tabular*}{0.97\textwidth}{@{\extracolsep{\fill}}lr}
      \textbf{#1} & \textbf{#2} \\  % 第一行：学校名称 & 地点
      \textit{#3} & \textit{#4} \\  % 第二行：专业名称 & 时间
      #5 &  % 第三行：GPA，仅左侧
    \end{tabular*}\vspace{-10pt}
  }
}


\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% \begin{center}
%     \textbf{\Huge \scshape 谈至存} \\ % Chinese Name
%     \vspace{5pt}
%     \textbf{生日:} 1998.06.06 \ \textbf{居住地:} 江苏苏州  \ \textbf{电话:} +(86) 13402536577 \\
%     \vspace{5pt}
%     \textbf{邮箱: }\href{mailto:tanzc9866@126.com}{tanzc9866@126.com} \ \href{https://github.com/SpartanTan}{\faGithub Github}\\ % 邮件
% \end{center}

\vspace*{-10mm}
\noindent
\begin{tabular}{@{}l@{}r@{\hspace{3cm}}l@{}}
    \multirow{3}[6]{*}{\textbf{\Huge Zhicun Tan(至存 \ 谈)}} & & \begin{tabular}[t]{@{}l@{}}
        \textbf{Birthday:} 06.06.1998 \\
        \textbf{Nationality:} \textbf{China} \\
        \textbf{Phone:} +(86) 13402536577 \\
        \textbf{e-mail:} \href{mailto:tanzc9866@126.com}{tanzc9866@126.com} \\
        \href{https://github.com/SpartanTan}{\faGithub} \ \href{www.linkedin.com/in/tanzhicun}{\faLinkedin}
    \end{tabular} \\
\end{tabular}

%--- Insert sections of resume here ---
\vspace{-5mm}
\section{Personal Statement} 
I hold a Master's degree in Autonomous Systems from Technical University of Denmark, having worked on C++ vehicle dynamics simulations, Matlab drone modelling \& control and Deep RL controller. My experience includes engineering in FSAE and various robotics competitions, demonstrating strong technical and teamwork skills.

\vspace{-3mm}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingExtended
      {Technical University of Denmark(DTU)}{Copenhagen, Denmark}
      {Master of Science in Engineering (MScEng), \textbf{Autonomous Systems}}{01.2021 -- 12.2023}  
      {GPA: 8.86/12; Courses: Linear control design, Perception for AS, Model-based system engineering}
  \resumeSubHeadingListEnd

  \vspace{0.5mm} % 调整这里的值以减少空间

  \resumeSubHeadingListStart
    \resumeSubheadingExtended
      {Chalmers University of Technology (exchange)}{Gothenburg, Sweden}
      {MSc in \textbf{System, Control and Mechatronics}}{09.2022 -- 12.2023}
      {Courses: Vehicle Motion Engineering, Modelling and Simulation, MPC}
  \resumeSubHeadingListEnd
  
  \vspace{0.5mm} % 调整这里的值以减少空间

  \resumeSubHeadingListStart
    \resumeSubheadingExtended
      {Nanjing Insitition of Technology}{Nanjing, Jiangsu}
      {BSc in \textbf{Mechatronics}}{09.2016 -- 06.2020}
      {GPA: 3.47, Rank in major: \textbf{10}/162}
  \resumeSubHeadingListEnd

%-----------Experience-----------
\section{Internship \& Work Experience}
\resumeSubHeadingListStart
  % \resumeSubheading
  % {Hyperview - Apetech Autonomous Racing Car}{ZZIC}
  % {Intern, Innovation and R\&D Department（\textbf{关键词：}Matlab，车辆横向控制，车辆动力学仿真，速度规划器）}{2024.10}
  % \resumeItemListStart
  %   % \resumeItem{参与开发基于惯导RTK定位的无人驾驶汽车横向控制实车调试及仿真}
  %   \resumeItem{负责建立车辆动力学模型，设计并联PID控制航向误差和横向轨迹误差，在仿真中验证可行性。最终 \\ 取得横向误差RMS小于2}
  %   \resumeItem{负责实现速度规划器。使用Menger方法计算赛道曲率，并根据最大横向加速度计算路段最大速度}
  %   \resumeItem{实现前向/后向调整的方法，确保速度规划符合车辆最大加/减速度限制，避免进弯前急减速和出弯后的急加速}
  %   \resumeItem{参与实车控制系统参数调试，所调车辆在株洲赛车场取得2分40秒的成绩}
  % \resumeItemListEnd

  \resumeSubheading
  {Hyperview - Apetech Autonomous Racing Car Project}{ZZIC}
  {Intern, Innovation and R\&D Department (\textbf{keywords:} Matlab, Vehicle Control, Speed Planner)}{10.2024}
  \resumeItemListStart
    \resumeItem{Responsible for developing the simulation with heading and lateral controller.}
    \resumeItem{Developed a speed planner using track curvature calculated by Menger method.}
    \resumeItem{Implemented forward/backward adjustments to ensure the planned speed is consistent with the vehicle's acceleration and deceleration limits.}
    \resumeItem{Participated in tuning the vehicle control system, achieving a lap time of 2'40''.}
  \resumeItemListEnd

  \resumeSubheading
  {\href{https://www.chalmersformulastudent.se/cfs-2023-car-margareta}{Chalmers Formula Student \faExternalLink}}{Chalmers}
    {Autonomous system engineer (\textbf{keywords:} C++, Gazebo, ROS, Vehicle dynamics modelling)}{09.2022 -- 08.2023}
    \resumeItemListStart 
      %\resumeItem{Developed a method for converting GPS coordinates to map coordinates, used to verify SLAM map accuracy.} 
      \resumeItem{Developed car state estimator using a LuGre tire model, implementing a 15-state Kalman filter.}
      \resumeItem{Developed a C++ plugin for \textbf{4wd vehicle dynamics simulation} using \textbf{RK4}.}
      \resumeItem{Solved conflict issues when migrated legacy simulator to latest Gazebo.}
      \resumeItem{Contributed to developing the launching system for launching autonomous systems with test options.} 
      \resumeItem{Assisted the team in \textbf{winnning} the   2023 FSG Driverless Cup and securing 7th place at FS East.} 
    \resumeItemListEnd
%   \resumeSubheading
  %   {凉善公益}{龙门乡塔哈村小学, 凉山彝族自治州}
  %   {\small 小学支教老师}{2024.02 -- 2024.06}
  %   \resumeItemListStart
  %     \resumeItem{二年级语文老师，班主任；三、四年级英语老师}
  %     \resumeItem{期末成绩全县排名17，同类学校排名第5}
%   \resumeItemListEnd

  % \resumeSubheading
  %   {苏州盖茨电子科技有限公司}{苏州，江苏}
  %   {电子研发实习生}{2020.09 -- 2020.10}
  %   \resumeItemListStart
  %     \resumeItem{参与调试基于S32K144的车载空压机FOC算法}
  %   \resumeItemListEnd
    
  \resumeSubheading
    {Off-robot robot lab}{NJIT, Nanjing}
    {MCU developer \& head of the lab (\textbf{keywords: }Embedded system, C, PID, Project Management)}{07.2017 -- 07.2018}
    \resumeItemListStart
      \resumeItem{Developed lane-following car on STM32, featuring camera/laser rangefinder tracking and robotic arm control.} 
      \resumeItem{Led the team to consecutive wins at provincial \& national level robot competitions.}
      \resumeItem{Got two utility patents granted, and completed a Challenge Cup project in the topic of pipeline robots.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Projects-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Reinforcement learning for robust
      mobile robot navigation control \; \href{https://1drv.ms/v/s!Al-YZOpjHxorgslaTIu4oeTj8TYROw?e=EflSJj}{\faVideoCamera} \;  \href{https://github.com/SpartanTan/RLATR}{\faGithub}}}{DTU}
      {Independent Developer (\textbf{keywords: }Kinematic modelling, Python, Reinforcement learning, PyQt)}{07.2023 -- 12.2023}
      \resumeItemListStart
        \resumeItem{Developed the kinematic model for a two-wheel drive robot and a  laser scanner module in Gymnasium.} 
        \resumeItem{Developed an algorithm to generate randomized paths, obstacles, and corridor walls for the training environment.}
        \resumeItem{Implemented reward functions for path tracking and obstacle avoidance. Testing and parameters tuning.}
        \resumeItem{Created a GUI tool for easy tweaking of training and environment parameters and for visualizing simulations.} \resumeItem{Trained the NN controller with PPO, achieving a 60\% success rate in unknown environments with obstacles.}
      \resumeItemListEnd
      
    \resumeSubheading
      {\textbf{Unmanned autonomous systems \; \href{https://1drv.ms/v/s!Al-YZOpjHxorgslZm5SJR7mVF_eoPw?e=4kRkvd}{\faVideoCamera} \;  \href{https://github.com/SpartanTan/31390-UAS-2022}{\faGithub}}}{DTU}
      {Project Developer (\textbf{keywords: }Matlab, quadcopter modelling, trajectory planning)}{06.2022 -- 06.2022}
      \resumeItemListStart
      \resumeItem{Created both nonlinear and linear models of the drone in Simulink for performance comparison.}
      \resumeItem{Developed position and altitude controllers in Simulink enabling set-point flight for quadcopter.}
      %\resumeItem{Built \textbf{quadcopter motion simulation module} using Simscape for testing controllers.}
      \resumeItem{Implemented path planning using A* in a 3D environment, successfully navigating a drone through a 3D maze.} 
      \resumeItem{Utilized polynomial optimization for trajectory planning, making the quadcopter navigate through 3D hoops.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{\href{https://1drv.ms/f/s!Al-YZOpjHxorgslbx6yg1s1e4ZGl1A?e=1DVmBG}{Awards \faExternalLink}}
    \resumeSubHeadingListStart

      \resumeSubheading
      {2023 Formula Student Germany Driverless Cup overall winner}{2023.08}
      {}{}
      \vspace{-4mm}

      \resumeSubheading
      {\textbf{First Award} in Intellect Vehicle Challenge}{06.2019}
      {}{}
      \vspace{-4mm}

      \resumeSubheading
      {Champion in 2018 China Engineering Robot Competition}{04.2018}
      {}{}
      \vspace{-4mm}

      % \resumeSubheading
      % {第八届江苏省机器人大赛 冠军 -（机器人越野项目：摄像头循迹、PID控制）}{2017.11}
      % {}{}
      % \vspace{-4mm}

      \resumeSubheading
      {First Award in 2018 China Robot Competition}{08.2017}
      {}{}
      \vspace{-4mm}
      % \resumeSubheading
      %   {National Junior Honor Society}{June 2023 -- Present}
      %   {}{}
      %   \resumeItemListStart
      %   \vspace{-4mm}
      %     \resumeItem{Award presented to students with outstanding achievements in academics, leadership, and community service.}
      %   \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------Courses-----------
% \section{Classes}
%  \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{
%     \vspace{1mm}
%      \textbf{Courses}{: AP Calulus BC, AP Chemistry, AP Physics, AP World History, AP U.S. History, AP Statistics, AP Literature} \\

%     }}
%  \end{itemize}

%-----------Skill and Interests-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    % \vspace{1mm}
     \textbf{Coding}{: Python, C/C++, Matlab/Simulink, Linux,  ROS, Docker, git} \\
    %  \vspace{1mm}
     \textbf{Autonomous Systems Expertise}{: PID/LQR/MPC, Deep RL, modelling \& control of drones, vehicles, and ROV} \\
    %  \vspace{1mm}
     \textbf{Language}{: IELTS 6.5 (Oral 7.0). Worked in international engineering team, demonstrating strong communication skills}

    }}
 \end{itemize}

%-----------Contact-----------
%  \begin{center}
% \small 123-456-7890 $|$
% \href{mailto:ADD EMAIL HERE@x.com}{\underline{andrew@gmail.com}} $|$
% \href{ADD LINKEDIN PAGE HERE}{\underline{linkedin.com/in/andrew}} 
% \end{center}

\end{document}
