\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm}

\usepackage{parskip} % This package handles paragraph formatting
\setlength{\parindent}{0pt} % Removes paragraph indentation

\begin{document}

% Your personal contact information
\begin{flushright}
\textbf{Zhicun Tan}\\
Tongjing South Road, Gusu District \\
Suzhou City, Jiangsu Province, China \\
tanzc9866@126.com \\
+(86) 13402536577\\
\today
\end{flushright}

\bigskip

% Employer's contact information
\begin{flushleft}
Hiring Manager \\
TOYOTA GAZOO Racing Europe \\
\end{flushleft}

\bigskip

\begin{flushleft}
Dear Hiring Manager,
\end{flushleft}

\bigskip

I am writing to express my enthusiasm for the Vehicle Dynamics Modeling Engineer position at TOYOTA GAZOO Racing Europe, as advertised on your official website.

\bigskip

My experience in modeling and simulating various systems through programming uniquely positions me for this role. At Chalmers Formula Student, I developed a vehicle dynamics-based race car simulator using C++, which played a critical role in our team winning the FSG 2023 Driverless Cup. Additionally, I have engaged in modeling, system identification, and controller design for quadcopters and underwater robots during my coursework. With extensive coding experience in these projects, I am confident I can quickly integrate and start developing within your existing frameworks as needed.

\bigskip

It's exciting to see that this opportunity also involves pushing the boundaries of innovation to advance the development of the GR series vehicles. My background in robotics and control systems can introduce new possibilities into vehicle simulations, potentially enhancing stability control, adaptive suspension systems, or wing controls. Additionally, my experience with deep reinforcement learning could contribute to finding optimal solutions under complex constraints. My extensive knowledge facilitates effective collaboration with subsystem teams, thereby enhancing integrative project outcomes.

\bigskip

I am a huge fan of the WRC, which is how I came to admire the GR Yaris WRC and TGR's commitment to excellence and innovation in motorsport. It is always exciting to develop top-tier technologies within such an organization. It would be an honor to translate these innovations into victories and enhance driving experiences for everyone.

\bigskip

Thank you for considering my application. I am eager to discuss how my background, skills, and enthusiasms align with the goals of TGR-E. I am available at your convenience for an interview.


\bigskip

Warm regards,

\bigskip

Zhicun Tan

\end{document}
